---
title: "Scrap"
output: html_notebook
---

Add price performance column to analysis
```{r}
ret <- read.csv(file = "price-performance.csv", header = FALSE, stringsAsFactors = FALSE)
ret$V1[1] <- "ACST-CA"
ret$V2 <- as.numeric(ret$V2)

df <- cbind(df, ret$V2[match(unlist(df$tick), ret$V1)])

names(df) <- c("tick", "investors", "loc", "val", "out", "cat", "ret") 

rm(ret)
```


Looking at the returns from the different catagories
```{r}
df.tmp <- df.company[!is.na(df.company$ret),]
df.tmp <- df.tmp %>% group_by(cat) %>% summarise(mean = weighted.mean(ret))

png(file = "returns-by-cat.png", width = 6, height = 3, units = 'in', res = 300)
ggplot(df.company) +
  #geom_col(aes(x = reorder(cat, -mean), y = mean), fill = "#2d465f") +
  geom_boxplot(aes(x = cat, y = ret)) +
  geom_jitter(aes(x = cat, y = ret), size = 2, width = 0.2,  colour = "#2d465f") +
  labs(y = "YTD Return (%)", x= "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
dev.off()

```

Returns by geography 
```{r}

png(file = "returns-by-geo.png", width = 6, height = 4, units = 'in', res = 300)
ggplot(df.investor) +
  geom_boxplot(aes(x = loc, y = w.mean_return), outlier.shape = NA) +
  geom_jitter(aes(x = loc, y = w.mean_return), size = 1, width = 0.2, colour = "#2d465f") +
  labs(y = "Weighted Average YTD Return (%)", x= "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
dev.off()

df.tmp <- df.investor[!is.na(df.investor$w.mean_return),]

mean(df.tmp$w.mean_return[df.tmp$loc == "Canada"])
mean(df.tmp$w.mean_return[df.tmp$loc == "United States"])
mean(df.tmp$w.mean_return[df.tmp$loc == "Other"])

```
df.catagory <- df %>% group_by(cat, loc) %>% summarise(count = n(), total = sum(val))

sum(df$val[(df$loc == "Canada" & df$cat == "Commercial Therapeutics")])
sum(df$val[(df$loc == "Canada" & df$cat == "Commercial Therapeutics")]) / sum(df$val[(df$loc == "Canada")])

sum(df$val[(df$loc == "Canada" & df$cat == "Consumer Health")])
sum(df$val[(df$loc == "Canada" & df$cat == "Consumer Health")]) / sum(df$val[(df$loc == "Canada")])

sum(df$val[(df$loc == "Canada" & df$cat == "Healthcare Services")])
sum(df$val[(df$loc == "Canada" & df$cat == "Healthcare Services")]) / sum(df$val[(df$loc == "Canada")])

sum(df$val[(df$loc == "Canada" & df$cat == "Medical Devices")])
sum(df$val[(df$loc == "Canada" & df$cat == "Medical Devices")]) / sum(df$val[(df$loc == "Canada")])

sum(df$val[(df$loc == "Canada" & df$cat == "Medical Supplies")])
sum(df$val[(df$loc == "Canada" & df$cat == "Medical Supplies")]) / sum(df$val[(df$loc == "Canada")])

sum(df$val[(df$loc == "Canada" & df$cat == "Therapeutic R&D")])
sum(df$val[(df$loc == "Canada" & df$cat == "Therapeutic R&D")]) / sum(df$val[(df$loc == "Canada")])

sum(df$val[(df$loc == "United States" & df$cat == "Commercial Therapeutics")])
sum(df$val[(df$loc == "United States" & df$cat == "Commercial Therapeutics")]) / sum(df$val[(df$loc == "United States")])

sum(df$val[(df$loc == "United States" & df$cat == "Consumer Health")])
sum(df$val[(df$loc == "United States" & df$cat == "Consumer Health")]) / sum(df$val[(df$loc == "United States")])

sum(df$val[(df$loc == "United States" & df$cat == "Healthcare Services")])
sum(df$val[(df$loc == "United States" & df$cat == "Healthcare Services")]) / sum(df$val[(df$loc == "United States")])

sum(df$val[(df$loc == "United States" & df$cat == "Medical Devices")])
sum(df$val[(df$loc == "United States" & df$cat == "Medical Devices")]) / sum(df$val[(df$loc == "United States")])

sum(df$val[(df$loc == "United States" & df$cat == "Medical Supplies")])
sum(df$val[(df$loc == "United States" & df$cat == "Medical Supplies")]) / sum(df$val[(df$loc == "United States")])

sum(df$val[(df$loc == "United States" & df$cat == "Therapeutic R&D")])
sum(df$val[(df$loc == "United States" & df$cat == "Therapeutic R&D")]) / sum(df$val[(df$loc == "United States")])

sum(df$val[df$cat == "Commercial Therapeutics"])
sum(df$val[df$cat == "Commercial Therapeutics"]) / sum(df$val)

sum(df$val[df$cat == "Consumer Health"])
sum(df$val[df$cat == "Consumer Health"]) / sum(df$val)

sum(df$val[df$cat == "Healthcare Services"])
sum(df$val[df$cat == "Healthcare Services"]) / sum(df$val)

sum(df$val[df$cat == "Medical Devices"])
sum(df$val[df$cat == "Medical Devices"]) / sum(df$val)

sum(df$val[df$cat == "Medical Supplies"])
sum(df$val[df$cat == "Medical Supplies"]) / sum(df$val)

sum(df$val[df$cat == "Therapeutic R&D"])
sum(df$val[df$cat == "Therapeutic R&D"]) / sum(df$val)

```


```{r}
df.canada <- df.investor[(df.investor$loc == "Canada"),]
df.us <- df.investor[(df.investor$loc == "United States"),]
```

Top Canadian Firms
```{r}
# By capital
tmp <- arrange(df.investor[df.investor$loc == "Canada",], desc(total))
tmp <- as.character(tmp$investors[1:10])

ylab = c(20, 40, 60, 80, 100, 120, 140)

png(file = "canadian-investors.png", width = 9, height = 4, units = 'in', res = 300)
ggplot(df[df$investors %in% tmp,]) +
  geom_col(aes(x = reorder(investors, -val, sum), y = val, fill = cat), colour = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "", y = "Total investment ($)", fill = "Catagory") +
  scale_y_continuous(labels = paste0(ylab, "M"), breaks = 10^6 * ylab) +
  scale_fill_manual(values=c("#eff3ff", "#A8A9AD", "#56B4E9", "#118AB2", "#2d465f", "#191919"))
dev.off()

df$tick[df$investors == "Mackenzie Financial Corp."]
df$tick[df$investors == "CI Investments, Inc."]
df$tick[df$investors == "Mawer Investment Management Ltd."]
df$tick[df$investors == "GLC Asset Management Group Ltd."]
df$tick[df$investors == "Fidelity (Canada) Asset Management ULC"]
df$tick[df$investors == "Fiera Capital Corp. (Investment Management)"]
df$tick[df$investors == "CIBC Asset Management, Inc."]
df$tick[df$investors == "BC Investment Management Corp."]
df$tick[df$investors == "RBC Global Asset Management, Inc."]
df$tick[df$investors == "EdgePoint Investment Group, Inc."]

# By number of investments
tmp <- arrange(df.investor[df.investor$loc == "Canada",], desc(count))
tmp <- as.character(tmp$investors[1:10])
tmp <- tmp[tmp != "Mackenzie Financial Corp."]

ylab = c(2, 4, 6, 8, 10, 12, 14, 16)

png(file = "canadian-investors2.png", width = 12, height = 8, units = 'in', res = 300)
ggplot(df[df$investors %in% tmp,]) +
  geom_col(aes(x = reorder(investors, -val, sum), y = val, fill = cat), colour = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "", y = "Total investment ($)", fill = "Catagory") +
  scale_y_continuous(labels = paste0(ylab, "M"), breaks = 10^6 * ylab) +
  scale_fill_manual(values=c("#eff3ff", "#A8A9AD", "#56B4E9", "#118AB2", "#2d465f", "#191919"))
dev.off()

```

Top American Firms
```{r}
tmp <- arrange(df.investor[df.investor$loc == "United States",], desc(total))
tmp <- as.character(tmp$investors[1:10])

ylab = c(20, 40, 60, 80, 100, 120, 140, 160)

png(file = "us-investors.png", width = 16.5, height = 6, units = 'in', res = 300)
ggplot(df[df$investors %in% tmp,]) +
  geom_col(aes(x = reorder(investors, -val, sum), y = val, fill = cat), colour = "grey") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "", y = "Total investment ($)", fill = "Catagory") +
  scale_y_continuous(labels = paste0(ylab, "M"), breaks = 10^6 * ylab) +
  scale_fill_manual(values=c("#eff3ff", "#A8A9AD", "#56B4E9", "#118AB2", "#2d465f", "#191919"))
dev.off()

df$tick[df$investors == "Fidelity Management & Research Co."]
df$tick[df$investors == "OrbiMed Advisors LLC"]
df$tick[df$investors == "Perceptive Advisors LLC"]
df$tick[df$investors == "RTW Investments LP"]
df$tick[df$investors == "Great Point Partners LLC"]
df$tick[df$investors == "HealthCor Management LP"]
df$tick[df$investors == "Baker Bros. Advisors LP"]
df$tick[df$investors == "Farallon Capital Management LLC"]
df$tick[df$investors == "Stadium Capital Management LLC"]
df$tick[df$investors == "Millennium Management LLC"]

# By weighted return on investments
tmp <- arrange(df.investor[df.investor$loc == "United States",], desc(w.mean_return))

tmp <- as.character(tmp$investors[1:10])

png(file = "us-investors2.png", width = 15, height = 6, units = 'in', res = 300)
ggplot(df[df$investors %in% tmp,]) +
  geom_point(aes(x = investors, y = ret, colour = cat, size = val)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "", y = "YTD return (%)", colour = "Catagory", size = "") +
  scale_colour_manual(values=c("#eff3ff", "#A8A9AD", "#56B4E9", "#118AB2", "#2d465f", "#191919")) +
  scale_size(guide = 'none')
dev.off()

```

```{r}
ylab = c(100, 200, 300, 400, 500, 600, 700, 800)

png(file = "company-firm-loc.png", width = 12, height = 5, units = 'in', res = 300)
ggplot(df.tmp) +
  geom_col(aes(x = reorder(tick, -val, sum), y = val, fill = loc)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "", y = "Total investment ($)", fill = "Location") +
  scale_y_continuous(labels = paste0(ylab, "M"), breaks = 10^6 * ylab) +
  scale_fill_manual(values=c("#A8A9AD", "#56B4E9", "#118AB2", "#2d465f", "#191919"))
dev.off()
```


```{r, echo=FALSE}
df.investor$loc <- as.character(df.investor$loc) 

df.investor$loc[!(df.investor$loc == "United States" | df.investor$loc == "Canada")] <- "Other"

ylab = c(20, 40, 60, 80, 100, 120, 140, 160, 180)

#png(file = "total-investments-v-number.png", width = 6, height = 3, units = 'in', res = 300)
ggplot(df.investor) +
  geom_point(aes(x = count, y = total, colour = loc), size = 2) +
  scale_y_continuous(labels = paste0(ylab, "M"), breaks = 10^6 * ylab) +
  scale_x_continuous(breaks = c(1:21)) +
  labs(y = "Total investment ($)", x = "Number of investments", colour = "Location") +
  #scale_color_manual(values=c("#CCCCCC", "#A8A9AD", "#56B4E9", "#118AB2", "#2d465f", "#191919"))
  scale_color_manual(values=c("#A8A9AD", "#118AB2", "#2d465f", "#191919"))
#dev.off()

```


```{r, echo=FALSE}
df.tmp <- df

df.tmp$loc <- as.character(df.tmp$loc) 

df.tmp$loc[!(df.tmp$loc == "United States" | df.tmp$loc == "Canada")] <- "Other"

ylab = c(400, 800, 1200, 1600, 2000)

#png(file = "investment-cat-by-loc.png", width = 6, height = 3, units = 'in', res = 300)
ggplot(df.tmp) +
  geom_col(aes(x = cat, y = val, fill = loc)) +
  labs(y = "Total investment ($)", x= "", fill = "Location") +
  scale_fill_manual(values=c("#A8A9AD", "#56B4E9", "#118AB2", "#2d465f", "#191919")) +
  scale_y_continuous(labels = paste0(ylab, "M"), breaks = 10^6 * ylab) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#dev.off()
```


